ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-08-31 paper/paper.tex
update :sparkles:

%"runningheads" enables:
%  - page number on page 2 onwards
%  - title/authors on even/odd pages
%This is good for other readers to enable proper archiving among other papers and pointing to content.
%Even if the title page states the title, when printed and stored in a folder, when blindly opening the folder, one could hit not the title page, but an arbitrary page. Therefore, it is good to have title printed on the pages, too.
\documentclass[a4paper]{llncs}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother
\usepackage{indentfirst}
%Even though `american`, `english` and `USenglish` are synonyms for babel package (according to https://tex.stackexchange.com/questions/12775/babel-english-american-usenglish), the llncs document class is prepared to avoid the overriding of certain names (such as "Abstract." -> "Abstract" or "Fig." -> "Figure") when using `english`, but not when using the other 2.
\usepackage[english]{babel}

\usepackage{amsmath}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stacked Generalization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The idea of Stacked Generalization \cite{stacking} is to use a group of first stage models to do prediction,
 followed by a second stage model using all the predictions from first stage models as input features.
 For task 2, we applied 2-folds stacking split by two different time frame
 and two 10-folds stacking on each time frame separately.

@@

\begin{enumerate}
 \item Split the training set in $N$ parts: $training_1, training_2, ..., training_N$

 \item Predict $testing$ and $training_1$ using $N-1$ folds ($training_2$, $training_3$, $...$, $training_N$) with first stage models

@@

 \item Train the second stage model based on the first stage predictions
\end{enumerate}

\begin{algorithm}
\caption{Stacking}\label{euclid}
\begin{algorithmic}[1]
\Procedure{MyProcedure}{}
\State $\textit{stringlen} \gets \text{length of }\textit{string}$
\State $i \gets \textit{patlen}$
\BState \emph{top}:
\If {$i > \textit{stringlen}$} \Return false
\EndIf
\State $j \gets \textit{patlen}$
\BState \emph{loop}:
\If {$\textit{string}(i) = \textit{path}(j)$}
\State $j \gets j-1$.
\State $i \gets i-1$.
\State \textbf{goto} \emph{loop}.
\State \textbf{close};
\EndIf
\State $i \gets i+\max(\textit{delta}_1(\textit{string}(i)),\textit{delta}_2(j))$.
\State \textbf{goto} \emph{top}.
\EndProcedure
\end{algorithmic}
\end{algorithm}

>>>>

%"runningheads" enables:
%  - page number on page 2 onwards
%  - title/authors on even/odd pages
%This is good for other readers to enable proper archiving among other papers and pointing to content.
%Even if the title page states the title, when printed and stored in a folder, when blindly opening the folder, one could hit not the title page, but an arbitrary page. Therefore, it is good to have title printed on the pages, too.
\documentclass[a4paper]{llncs}
%\usepackage{algorithm}
%\usepackage[noend]{algpseudocode}
\usepackage[linesnumbered,ruled]{algorithm2e}
\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother
\usepackage{indentfirst}
%Even though `american`, `english` and `USenglish` are synonyms for babel package (according to https://tex.stackexchange.com/questions/12775/babel-english-american-usenglish), the llncs document class is prepared to avoid the overriding of certain names (such as "Abstract." -> "Abstract" or "Fig." -> "Figure") when using `english`, but not when using the other 2.
\usepackage[english]{babel}
\usepackage{amsmath}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stacked Generalization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The idea of Stacked Generalization \cite{stacking} is to use a group of first stage models to do prediction,
 followed by a second stage model using all the predictions from first stage models as input features.

@@

\begin{enumerate}
 \item Split the training set in $N$ parts: $training_1, training_2, ..., training_N$ using stratified or random split

 \item Predict $testing$ and $training_1$ using original features from $N-1$ folds ($training_2$, $training_3$, $...$, $training_N$) with first stage models

@@

 \item Train the second stage model based on original features and first stage predictions
\end{enumerate}
%

% \begin{algorithm}
%     \SetKwInOut{Input}{Input}
%     \SetKwInOut{Output}{Output}
%
%     \underline{function Stacking} $(df\_train, df\_test, df\_train\_target, num\_folds, stacking\_index,model$)\;
%     \Input{$df\_train$: Dataframe for training features \newline
%            $df\_test$: Dataframe for testing features \newline
%            $df\_train\_target$: Target variable for training data \newline
%            $num\_folds$: number of folds \newline
%            $model$: Prediction Model with method fit and predict
%            }
%     \Output{Stacking Feature}
%
%     \emph{// Randomly split dataset}\\
%
%
%
%
%
%     \For{$k=1$ {\bfseries to} $num\_folds$ }{
%
%         tmp_valid = df_train
%         tmp_train = df_train
%
%
%     }
%
%     \eIf{$b=0$}
%       {
%         return $a$\;
%       }
%       {
%         return Euclid$(b,a\mod b)$\;
%       }
%     \caption{Stacking algorithm}
% \end{algorithm}

We only applied stacking on task 2.
We tried two stacking method seperately
\begin{enumerate}
 \item 2-folds stacking split by two different time frame

 \item 10-folds stacking after merging two time frame
\end{enumerate}

Since stacking index must be fixed in order to avoid leakage, we can only choose either 2-folds or 10-folds.
Although 10 folds is a common choice as it provides minmial information loss, we finally choose two folds for two reasons:
\begin{enumerate}
 \item The training data is a combination data in two periods. It provides out-of-period stacking feature split by time, which is useful to avoid overfitting.

 \item Both stacking provides improvement on local CV, but 10 folds show discrepancy betweem CV and 30\% of testing data.
\end{enumerate}

In practice, a diversified combination of stacking features from different algorithms (KNN, RandomForest, SVM, NN, etc.)
will usually outperform stacking using only one algorithm.
Since we only used xgboost here, we tried to compensate this by building several stacking features using randomized parameters.

Fig. 1 shows the AUC perfomance of CV result and 30\% of testing data. Although there's a difference of AUC between local CV and 30\% of testing data,
there is a strong correlation between CV and testing data. The AUC is higher when stacking is applied and result keep improving when we used more stacking features.

\begin{figure}[ht!]
\centering
\includegraphics[width=110mm]{Rplot.png}
\caption{AUC of 5folds CV result and 30\% testing data using different number of stacking features \label{overflow}}
\end{figure}

% \begin{algorithm}
% \caption{Stacking}
% \begin{algorithmic}
% \Procedure{MyProcedure}{}
% \State $\textit{stringlen} \gets \text{length of }\textit{string}$
% \State $i \gets \textit{patlen}$
% \BState \emph{top}:
% \If {$i > \textit{stringlen}$} \Return false
% \EndIf
% \State $j \gets \textit{patlen}$
% \BState \emph{loop}:
% \If {$\textit{string}(i) = \textit{path}(j)$}
% \State $j \gets j-1$.
% \State $i \gets i-1$.
% \State \textbf{goto} \emph{loop}.
% \State \textbf{close};
% \EndIf
% \State $i \gets i+\max(\textit{delta}_1(\textit{string}(i)),\textit{delta}_2(j))$.
% \State \textbf{goto} \emph{top}.
% \EndProcedure
% \end{algorithmic}
% \end{algorithm}
